Summary of the things that I learned

### 2023-04-19 transcript/summary.tex
Add two talks, move the summary to a subdirectory

  \section{Default API for any \texttt{object}}
  \begin{itemize}
    \item \texttt{object\_data}: A definition for the data of the object;
    \item \texttt{make\_object\_data}: A function to make the object data out of its parts;
    \item (Coercions from \texttt{object\_data} to some of its parts;)
    \item (Explicit functions to access the constituents;)
    \item \texttt{is\_object}: A definition for the properties of the object;
    \item \texttt{make\_is\_object}: A function to make the properties part of the object;
    \item \texttt{make\_object}: A function to make the object out of its data and property components;
    \item (A coercion from the object to its data;)
    \item A lemma that the properties form a proposition.
    \item \texttt{object\_eq}: A lemma about sufficient (and necessary) conditions for two terms of type \texttt{object} to be equal (usually some conditions on the constituents of \texttt{object\_data});
  \end{itemize}

@@

>>>>

  \section{Default API for any \texttt{object}}
  \begin{itemize}
    \item \texttt{object\_data}: A definition for the data of the object;
    \item \texttt{make\_object\_data}: A function to make the object data out of its parts;
    \item (Coercions from \texttt{object\_data} to some of its parts;)
    \item (Explicit functions to access the constituents;)
    \item \texttt{is\_object}: A definition for the properties of the object;
    \item \texttt{make\_is\_object}: A function to make the properties part of the object;
    \item \texttt{make\_object}: A function to make the object out of its data and property components;
    \item \texttt{object}:
    \item (A coercion from the object to its data;)
    \item (\texttt{object\_has\_property}: Explicit functions to access the properties;)
    \item \texttt{is\_object\_isaprop}: A lemma that the properties form a proposition;
    \item \texttt{object\_eq}: A lemma about sufficient (and necessary) conditions for two terms of type \texttt{object} to be equal (usually some conditions on the constituents of \texttt{object\_data});
  \end{itemize}

@@

  \section{Things I would have liked to know at the start}
  The fact that if a rewrite does not succeed because a lemma has a slightly different (folded or unfolded) description, we can just force its form like \texttt{rewrite (lemma : form1 = form2)}.

  Setting just one implicit argument like \texttt{action (n := 5)}.

  The fact that instead of finishing a (sub)proof with \texttt{[tactic]. apply idpath.}, one can finish it with \texttt{now [tactic].}.

  \section{Things that I would like to have a standard for}
  \begin{itemize}
    \item Naming (of folders, files, terms): what abbreviations are allowed? In what order do words appear? How are words separated? How are names capitalized?
    \item Documentation headers in files.
    \item In which cases do we want to use unicode?
    \item In which cases do we want definitions to be (fully) typed?
    \item In which cases do we want accessor functions for all data and properties?
  \end{itemize}

  No lines should have trailing whitespace and all files should have a trailing newline.
